The analogy of the cohort-equations paradigm to the compartmental epidemic models

### 2021-05-31 cohort.tex
addressing the comments
adding minor stuff

\item
Calculating the next-generation vector $\vec G$ is 
(\ali{feels odd here, help! $\vec G$ here is a vector with elements of the eigenvalues of the \citep{van2002reproduction}'s next-generation matrix $FV^{-1}$. 
Also check Heesterbeek work what he calls this}) 
\begin{equation}
\label{eq:ng} %next generation
\vec G = FV^{-1} = \int_0^\infty \vec K(\tau) d\tau.
\end{equation}
Note that $\R$ would be the dominant element of $\vec G$.
\end{enumerate}
Note that in the compartment framework \cite{van2002reproduction}, steps 2 and 3 are combined.
%%%%%%%%%%%%%%%%%%%%
\section{Examples}

@@

%%%%%%%%%
\noindent
{\bf Example 3. SIR with testing and isolation;}
The model can be summarized in the form of following matrices.
\begin{align}
\label{FV}
F =&\beta/N_0 \left[ \begin {array}{c} S\_u^* \\ (1-\theta\_w)S\_n^* \\ 0 \\ 0 \end {array} \right]
        \left[ \begin {array}{cccc} 1, \, 1-\theta\_w, \, 1-\theta\_w, \, 1-\theta\_c \end {array} \right], \text{and}\\  V=&
 \left[ \begin {array}{cccc}  
\hat F_I+\gamma&-\omega&0&0\\
-(1-p_I)\hat F_I&\omega+\gamma&0&0\\
-p_I \hat F_I&0&\omega+\gamma&0\\
0&0&-\omega&\gamma
\end {array} \right].
\end{align}

@@

{\it Step 3;} The next-generation vector is $\vec G$ as follows.
\begin{align}
\vec G=&\int_0^\infty \vec K(\tau) d\tau\\
=&
\end{align}
%%%%%%%%%%%%%%%%%%%%

>>>>

\item
Calculating the next-generation vector $\vec G$ is 
(\ali{feels odd here, help! $\vec G$ here is a vector with elements of the eigenvalues of the \citep{van2002reproduction}'s next-generation matrix $FV^{-1}$. 
Also check Heesterbeek work what he calls this}) 
\begin{equation}
\label{eq:ng} %next generation
\vec G = FV^{-1} = \int_0^\infty \vec K(\tau) d\tau.
\end{equation}
Note that $\R$ would be the dominant element of $\vec G$.
\end{enumerate}
Note that in the compartment framework \cite{van2002reproduction}, steps 2 and 3 are combined.

%%%%%%%%%%%%%%%%%%%%
\section{Examples}

@@

%%%%%%%%%
\noindent
{\bf Example 3. SIR with testing and isolation;}
The model can be summarized in the form of following matrices.
\begin{align}
\label{FV}
F =&\beta/N_0 \left[ \begin {array}{c} S\_u^* \\ (1-\theta\_w)S\_n^* \\ 0 \\ 0 \end {array} \right]
        \left[ \begin {array}{cccc} 1, \, 1-\theta\_w, \, 1-\theta\_w, \, 1-\theta\_c \end {array} \right], \text{and}\\  
V=& \left[ \begin {array}{cccc}  
\hat F_I+\gamma&-\omega&0&0\\
0&\omega+\gamma&0&0\\
-\hat F_I&0&\omega+\gamma&0\\
0&0&-\omega&\gamma
\end {array} \right].
\end{align}

@@

{\it Step 3;} The next-generation vector is $\vec G$ as follows.
\begin{align}
\vec G=&\int_0^\infty \vec K(\tau) d\tau\\
=&
\end{align}
%%%%%%%%%%%%%%%%%%%%
\section{Ideas-Unknowns}
- Collapsing the vectorized kernek $\vec K(\tau)$ into a scalar function of time.

- We have 3 cases; (i) the general case where each box in $\vec I$ been pulled into others boxes of $\vec I$  (ii) simple case where we have 1 group eg. linear chain (iii) intermediate case where we have more than 1 entry point into $\vec I$ but mediated through a unitary FoI like SIR with testing.

- SIR with testing;

- Linear Algebra refreshing: \url{https://see.stanford.edu/materials/lsoeldsee263/11-eig.pdf}
